A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
The algorithm returns the mapping, not its size
Nicer sentence about null entry in adj matrix

We start our search at the function $\FuncSty{McSplit}$ (\lineref{McSplitFun}),
with graphs $\graphG$ and $\graphH$ as inputs.  This function returns the size of the
largest mapping.  In \lineref{FirstExpandCall} the initial call is made to
$\FuncSty{search}$; at this point we have a single label-class containing all
vertices, and the mapping $M$ is empty.

@@

\paragraph{Undirected with edge labels} Each adjacency matrix entry contains an
edge label, or a null entry (non-adjacent) $0$.  We use \cref{labDirAlg}, by
letting $L$ be the union of $\{0\}$ with the set of all labels that appear in
the input graphs. Since there may be up to $g + h$ distinct labels, the loop in
\cref{labDirAlg} may execute up to $g + h$ times, resulting in $\BigO{(g+h)^2}$
time complexity per search node.  To achieve $\BigO{(g+h) \log (g+h)}$ time
complexity per search node, we can modify the algorithms to use sorting rather
than explicitly looping over all label classes, as follows.  First, run lines
17-19 of \cref{McSplitAlg} to create a new label-class of vertices that are
not adjacent to $v$ or $w$, and remove these vertices from $\langle \setG',\setH'
\rangle$.  Next, sort $\setG'$ and $\setH'$ in ascending order of the label on the edge
from $v$ or $w$ to each vertex. We can then create the label classes
corresponding to each edge label by simultaneously traversing $\setG'$ and $\setH'$
from left to right.

>>>>

We start our search at the function $\FuncSty{McSplit}$ (\lineref{McSplitFun}),
with graphs $\graphG$ and $\graphH$ as inputs.  This function returns a mapping of
maximum cardinality.  In \lineref{FirstExpandCall} the initial call is made to
$\FuncSty{search}$; at this point we have a single label-class containing all
vertices, and the mapping $M$ is empty.

@@

\paragraph{Undirected with edge labels} Each adjacency matrix entry contains an
edge label, or a null entry $0$ indicating that no edge is present.  We use \cref{labDirAlg}, by
letting $L$ be the union of $\{0\}$ with the set of all labels that appear in
the input graphs. Since there may be up to $g + h$ distinct labels, the loop in
\cref{labDirAlg} may execute up to $g + h$ times, resulting in $\BigO{(g+h)^2}$
time complexity per search node.  To achieve $\BigO{(g+h) \log (g+h)}$ time
complexity per search node, we can modify the algorithms to use sorting rather
than explicitly looping over all label classes, as follows.  First, run lines
17-19 of \cref{McSplitAlg} to create a new label-class of vertices that are
not adjacent to $v$ or $w$, and remove these vertices from $\langle \setG',\setH'
\rangle$.  Next, sort $\setG'$ and $\setH'$ in ascending order of the label on the edge
from $v$ or $w$ to each vertex. We can then create the label classes
corresponding to each edge label by simultaneously traversing $\setG'$ and $\setH'$
from left to right.
